Figures

### 2018-07-12 figures/08_maps.Rmd
make colors indicate connecitivity not metric magnitude in maps

# pull the lower partition group as an sf object
get_sub <- function(dt, col_name, split_value){
  coordinatize(
    dplyr::filter(dt, UQ(rlang::sym(as.character(col_name))) <= split_value), 
    "lat", "long")
}

lower_iws_maps <- lapply(which(partition_splits$scale == "iws"), 
                         function(x) {
                           nes_sub <- get_sub(nes_iws, 
                                            partition_splits[x, "iws_names"],
                                            partition_splits[x, "splits"])

@@

lower_nws_maps <- lapply(which(partition_splits$scale == "nws"), 
                         function(x) {
                           nes_sub <- get_sub(nes_nws, 
                                              partition_splits[x, "nws_names"],
                                              partition_splits[x, "splits"])

@@

>>>>

metric_order_key <- data.frame(
  pnames2 = c("sr", "bf", "la", "sd", "cd", "ll"), 
  higher_connectivity = c("higher", "higher", "higher", "lower", "higher", "higher"))

partition_splits <- left_join(partition_splits, metric_order_key)

# pull the lower partition group as an sf object
lower_iws_maps <- lapply(which(partition_splits$scale == "iws"), 
                         function(x) {
                           # x <- which(partition_splits$scale == "iws")[3]
                           nes_sub <- get_sub(nes_iws, 
                                          partition_splits[x, "iws_names"],
                                          partition_splits[x, "splits"], 
                                          partition_splits[x, "higher_connectivity"])

@@

lower_nws_maps <- lapply(which(partition_splits$scale == "nws"), 
                         function(x) {
                           # x <- which(partition_splits$scale == "nws")[1]
                           nes_sub <- get_sub(nes_nws, 
                                          partition_splits[x, "nws_names"],
                                          partition_splits[x, "splits"], 
                                          partition_splits[x, "higher_connectivity"])

@@

partition_splits$pnames2 <- factor(partition_splits$pnames2, 
                                   levels = c("ll", "cd", "sd", "la", "bf", "sr"))
